=== Calculating distance in ML ===

* Why we care about Correlation or Covariance matrix?
Good question. In Machine Learning every algorithm tries to calculate distance
(you can name anything: error, for example). Distance could be between predicted
label and true label. In general we want to know how well we did. Also we would
like to know is there any relation between data and label (as in any relation
between two variables)

==== Correlation and Covariance matrix ====

“Covariance” and “correlation” are similar concepts; the correlation between
two variables is equal to their covariance divided by their variances

Correlation is computed as part of the covariance matrix, S.

For a dataset of m samples, where the ith sample is denoted as x_i, the
covariance matrix S is computed as:
        m
s = 1/m ∑ (x_i - mu) (x_i - mu)^T
       i=1

where m = # of samples, mu = Avg of data

A very good explanation of Covariance matrix you can find in here:
https://stats.stackexchange.com/questions/18058/how-would-you-explain-covariance-to-someone-who-understands-only-the-mean
I liked second answer better.

* Take 2
http://www.visiondummy.com/2014/04/geometric-interpretation-covariance-matrix/
-> Something to note:
variance can only be used to explain the spread of the data in the directions
parallel to the axes of the feature space. The diagonal spread of the data is
captured by the covariance.

For 2D data, we thus obtain \sigma(x,x), \sigma(y,y), \sigma(x,y) and \sigma(y,x).
These four values can be summarized in a matrix, called the covariance matrix:

 \begin{equation*} \Sigma = \begin{bmatrix} \sigma(x,x) & \sigma(x,y) \\[0.3em] \sigma(y,x) & \sigma(y,y) \\[0.3em] \end{bmatrix} \end{equation*}


==== References ====
http://mccormickml.com/2014/07/21/mahalanobis-distance/
http://www.visiondummy.com/2014/04/geometric-interpretation-covariance-matrix/
https://stats.stackexchange.com/questions/18058/how-would-you-explain-covariance-to-someone-who-understands-only-the-mean
